---
title: "Toronto marriages by the months"
subtitle: "Is the frequency indeed uniform, or is something else going on?"
author: 
  - Andrew Goh
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Abstract: Does the current time of year affect one (or, more accurately, two)'s inclinations towards marriage? 
This paper aims to look at this question by comparing raw marriage data from Toronto to the
theoretical uniform distribution that the null hypothesis proposes."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#| echo: false
library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
```

```{r}
#| label: fig-marriage
#| fig-cap: Marriages by date
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```
Here is my data graph about marriages in Toronto! Notice how in @fig-marriage we can see that marriages follow a 'spikey' trend, with certain extremely high data points compared to other, much lower ones. If the distribution were uniform, we would be seeing, as the name suggests, a more uniform distribution of data points in the scatter plot, so this is pretty suggestive evidence that the true distribution of the population parameter is not, in fact, a uniform distribution.
\newpage


# References

@dplyr
@opendatatoronto
@talia
@thereferencecanbewhatever

